ASR-Output-Correcting Webapp After 6 Years

### 2018-03-25 2018-tsd-brno/webapp.tex
eh nix
bla bla redux

We use React as the view library and Redux for state management. The good thing
about Redux is that it makes it easy to keep minimal state as the single source
of truth and everything that can be computed is computed, while avoiding
needless calculations. This is of course nothing new -- basically it is what we
know from database design as the normal representation. Also in our case, this
approach makes the program more predictable, less error-prone and, as the modern
programming jargon lovingly expresses, {\em easier to reason about}.

We are squeezing as much juice from these fruits as we can.

Among the states the app can enter is simple playback, inspecting a word,
transcribing a segment and replaying the selected audio span. Now, the only
thing we actually store is the sub

>>>>

We use React as the view library and Redux for state management. The good thing
about Redux is that it makes it easy to keep minimal state as the single source
of truth and everything that can be computed is computed, while avoiding
needless calculations. This is of course nothing new -- basically it is what we
know from database design as the normal representation. It is the first time
this approach reached the web front-end in such degree of popularity though.

Also in our case, this approach makes the program more predictable, less
error-prone and, as the modern programming jargon lovingly expresses, {\em
easier to reason about}. But some of our features make this a bit complicated.

Among the states the app can enter is simple playback, inspecting a word,
transcribing a segment and replaying the selected audio span. Now, the only
relevant things we actually store is the redux state are:
\begin{enumerate}
\item{
    The array of transcription words, each of which bears the flag whether it is
    automatically or manually transcribed. This defines the manual - automatic
    chunks of words that in turn define the HTML elements wrapping them.
}
\item{
    The beginning and end of the selection in terms of chunk number and
    character offset in the chunk, which is basically what we get from the DOM
    upon a \texttt{mouseup} event.
}
\item{Whether playback is running and the current position.
\end{enumerate}

Whether a word is marked or a segment is being edited is determined solely by
the boundaries of the selected words. If there is a selection and the beginning
and end are identical, it means a word was simply clicked and its detail is
shown (it is {\em marked}). If the boundaries span at least one character, then
all words that intersect this span are {\em selected} for correction.

Simple as it sounds, a slight problem arises when a correction is accepted and
the corrected subtitles are merged into the view. In the time after the
correction is accepted and reflected in the redux state, but before the new
chunks are rendered in the document, selection changes cannot be reliably mapped
to logical chunks. Simple null defaults solve this problem.

\section{Future Work}

Next up in our to-do list is releasing the application to wider public and
researching the
